Handbook streamFind: backend

### 2023-02-13 README.Rmd
Added logos to README.
Updated group logo in README
Continuation of R6 implementation 13

The streamFind package is a backend (code based) and frontend ([shiny](https://shiny.rstudio.com/) app) platform for assembly of modular workflows to support spectrometric and spectroscopic data processing. The major focus of streamFind is data processing for environmental and quality studies of the water cycle. The streamFind package aims to stimulate the use of advanced data analysis (e.g., non-target screening and statistical analysis) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functionalities (modules).

@@

For installation of the streamFind package, it is recommended to firstly ensure that the dependencies are currently installed. Several existing R packages and external functionalities are used in streamFind for various processing steps. A major dependency of streamFind is the [patRoon](https://github.com/rickhelmus/patRoon) R package. The patRoon package combines several functionalities for basic and advanced data processing and can be used interchangeably with streamFind.

@@

## Back-end usage

>>>>

The R package `streamFind` (this repository) is the back-end platform for the streamFind project entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle". The streamFind project is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The major focus of `streamFind` is data processing for environmental and quality studies. The `streamFind` R aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functions or modules (see vignettes for more information).

```{r, echo=FALSE, out.width = '100%', fig.align='center'}
knitr::include_graphics("inst/extdata/logo_group.png")
```

@@

For installation of the `streamFind` R package, it is recommended to firstly ensure that the dependencies are currently installed. Several existing R packages and external software are used in `streamFind` for various processing steps. A major dependency of `streamFind` is the [patRoon](https://github.com/rickhelmus/patRoon) R package. The `patRoon` R package combines several tools for basic and advanced data processing and can be used interchangeably with `streamFind`.

@@

## Backend usage

### 2023-02-13 handbooks/Handbook_backend_streamFind.Rmd
Continuation of R6 implementation 13

---
title: "Handbook streamFind: back end"
author: "Ricardo Cunha"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    theme: paper
    css: "Handbook_backend_streamFind.css"
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Handbook streamFind: backend"
author: "Ricardo Cunha"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    theme: paper
    css: "Handbook_backend_streamFind.css"
editor_options: 
  chunk_output_type: console
---
